Deciding to Disclose

### 2015-06-15 Background.tex
Simulation schedule

The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which simply put, states that the worth of an action is the probability of each outcome, multiplied by the subjective gain or loss it delivers.

>>>>

The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}. Utility in this sense is the subjective value of an outcome, often expressed in monetary terms, and expected utility incorporates the uncertainty of obtaining that outcome. This is expressed by taking the expected utility of an outcome to be the probability of the outcome occurring, multiplied by the subjective value of it.

### 2015-06-15 Model.tex
Simulation schedule

In this section we outline the disclosure game model, and give details of the four decision rules that will be examined in this paper, but begin with a brief sketch of a pregnancy in terms of encounters between a pregnant woman and a midwife.

Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.

Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted. In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.

@@

\begin{table}
\center
\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}

\caption{Payoff matrices\label{tab:Payoff-matrix}}
\end{table}

Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.

@@

Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}. This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Arrows correspond to two moves by nature, followed by women, and midwives respectively. Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types. For midwives, referral is shown by a heavier arrow. Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}

\label{fig:simple_tree}
\end{figure}

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}

\label{fig:zoom_tree}
\end{figure}

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
\vskip
\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

\label{fig:decision_problems}
\end{figure}

@@

\begin{algorithm}
\begin{algorithmic}
\State n=1, action=none
\While{action is none}
\State Calculate the nth most common outcome following each action.
\State Sort actions by the value of the nth most common outcome.
\If{clear winner} \State action = best \EndIf
\State n = n + 1
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

@@

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations for a pair \(i\).

@@

\subsection{Information Sharing}
\label{sub:info_sharing}

>>>>

In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with simulation psuedocode in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.

\subsection{Model Construction Approach}
\label{sec:model_design}

The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious. There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process. We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.

Transitioning from the resulting game, to a set of decision problems is a relatively simple task. We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance. As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.

These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game. Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects. In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.

@@

@@

@@

\begin{algorithm}
\begin{algorithmic}
\State $n \gets 1, action \gets none$
\While{$action = none$}
\State Calculate the $n$th most common outcome following each action.
\State Sort actions by the value of the $n$th most common outcome.
\If{clear winner} \State $action \gets best$ \EndIf
\State $n \gets n + 1$
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

@@

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).

@@

\subsection{Social Learning}
\label{sub:info_sharing}
